\textsf{Are frontier models superhuman chemists?}

### 2024-03-18 src/tex/ms.tex
implemented subset analysis

While many of the existing benchmarks are designed around \gls{mcq}, this does not reflect the reality of chemistry education and research.
For this reason, \chembench samples both \gls{mcq} and open-ended questions (\variable{output/mcq_questions.txt} \gls{mcq} questions vs. \variable{output/non_mcq_questions.txt} open-ended questions).
As one might expect, most questions are difficult to read according to the Flesch–Kincaid readability test (\variable{output/flesch_kincaid_reading_ease.txt}).\cite{kincaid1975derivation}

@@

\paragraph{Models}
\subparagraph{Completion models}
We used \texttt{Galactica-120b}\cite{taylor2022galactica} with the default settings

\subparagraph{Instruction-tuned models} \texttt{Claude 2} \texttt{Claude3 (Opus)}\cite{anthropicClaudeModelFamily2024}
\texttt{GPT-4}\cite{openai2024gpt4}
\texttt{GPT-3.5-turbo}\cite{brown2020language}
\texttt{Gemini Pro}\cite{gemini}
\texttt{Mixtral-8x7b}\cite{jiang2024mixtral}
\texttt{Llama2-70b}\cite{touvron2023llama}
\texttt{pplx-7b-chat}

@@

>>>>

While many of the existing benchmarks are designed around \gls{mcq}, this does not reflect the reality of chemistry education and research.
For this reason, \chembench samples both \gls{mcq} and open-ended questions (\variable{output/mcq_questions.txt} \gls{mcq} questions vs. \variable{output/non_mcq_questions.txt} open-ended questions).
%As one might expect, most questions are difficult to read according to the Flesch–Kincaid readability test (\variable{output/flesch_kincaid_reading_ease.txt}).\cite{kincaid1975derivation}

@@

\paragraph{Models}
\subparagraph{Completion models}
We used \texttt{Galactica-120b}\cite{taylor2022galactica} with the default settings.

\subparagraph{Instruction-tuned models} In addition, we used \texttt{Claude 2}, \texttt{Claude3 (Opus)},\cite{anthropicClaudeModelFamily2024} \texttt{GPT-4},\cite{openai2024gpt4} \texttt{GPT-3.5-turbo},\cite{brown2020language}
\texttt{Gemini Pro},\cite{gemini}
\texttt{Mixtral-8x7b}\cite{jiang2024mixtral}
\texttt{Llama2-70b},\cite{touvron2023llama}
\texttt{pplx-7b-chat}

@@

The authors thank Julian Kimmig for feedback on the web app.
